Contextual Identity: Towards Usable Privacy

### 2013-03-06 paper.tex
check connective tissue

\label{sec:examples}
\subsection{Redistributing information out of context}
Redistributing information out of its original context often leads to
embarrassment~\cite{nissenbaum}.  In November 2007, Facebook Beacon allowed
third-party sites to publish purchases, travel bookings, movie rentals and more
to the user's activity stream.  Because of poor opt-out and lack of visibility
into what was being published, user outcry was
immediate~\cite{mccarthy,nakashima}.  In December 2007, Google Reader exposed
RSS feeds of user-marked news stories to the user's Google Talk contacts, which
includes everyone with whom a user has chatted whether they be co-workers,
supervisors, or friends. Although this feed was always public, prior to this
launch it was not discoverable, leading to a bad experience for many
users~\cite{helft}. In February 2010, Google Buzz launched, a product that
exposed the user's most frequent Gmail and Google Talk contacts and their
publicly available (through previously less discoverable) news and photos.  The
combination of exposing contacts (which could include abusive ex-husbands,
co-workers, and friends), as well as aggressively linking photos and news
items, resulted in a huge backlash~\cite{fugitivus,buzz}. In September 2012,
Facebook imported old wall posts from 2008 into the new Timeline interface.
Although wall posts were always visible from profile pages, the new Timeline
interface brought old wall posts, which users used to treat as private messages
before the advent of ``Like'' and comment buttons, to the attention of an
audience that the user never anticipated~\cite{timeline}.

@@

The following examples illustrate how users keep their identities separate.

@@

Using multiple browsers is a useful technique for managing multiple accounts.
Some services support multiple accounts but not multiple login (e.g.,
Twitter). For services that do (e.g., many Google services), the user interface
may be so confusing that it leads to errors, so the best recommendation may be
to use multiple browsers~\cite{yegge}.\footnote{Using multiple
browsers as an alternative to multiple login:
\url{https://support.google.com/accounts/bin/answer.py?hl=en&answer=179235}}
For users who want to separate work and
personal browsing, using multiple browsers is the easiest solution.

@@

Many users have multiple devices and many use them for different purposes.
Sometimes the difference in purpose is due to the nature of the device (e.g.,
GPS and mapping software are probably more often used in mobile devices) and
some may be due to policy (e.g., personal browsing is limited to a personal
laptop). Using multiple devices implicitly creates multiple browser states and
thus multiple identities.  However, these identities may still be linked
through authentication data or other techniques.%~\cite{aol}

@@

Several browsers support separation of profile data, including cookies,
history, passwords, and other local storage. Firefox 
%\url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}.}
and Chrome support multiple profiles, though neither of these is very
discoverable or easy to use.\footnote{Chrome:
\url{https://support.google.com/chrome/bin/answer.py?hl=en&answer=2364824},
Firefox: \url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}} The
threat model does not include users with malicious intent in the same
household.

@@

Users can explicitly create links between contextual identities, e.g.  linking
to their blog from their Flickr profile, or resharing a blog post via Twitter.
It is also easy to implicitly create links between contextual identities,
sometimes accidentally: generating two isomorphic graphs at different services
is often enough to re-identify an individual~\cite{narayanan1}. The plethora of
cross-posting software available suggests that users often want to link
identities.

Building reputation online is a long and arduous process; a user who has built
up high credibility in one social network may want to transfer that credibility
when using a new service by using the same identifier or somehow proving in the
new service that they control other credible identities.  The advent
of verified account mechanisms in Twitter, Google Plus and Facebook indicates
that this problem is on the rise.

@@

All five major browsers (Firefox, Chrome, Safari, Internet Explorer, and Opera)
offer synchronizing some set of browser data across devices, with varying
degrees of success. Multiple cross-browser applications also exist to
synchronize bookmarks and passwords.\footnote{Bookmark sync: \url{xmarks.com}, password sync: \url{lastpass.com}}

@@

\paragraph{Service settings} Service configurations such as Facebook friends,
Google circles and privacy settings are intended for users to self-manage
privacy and identity. However, shifting privacy settings and complex,
interacting features make these configurations unpredictable for many users.

@@

Service providers are highly incentivized to make linking identities easy;
more tools to help separate and curate identities are necessary. Without
knowing more about how users think about identity, we concentrate solely on
automating manual processes that users already perform.

@@

\paragraph{Expiring posts}
Humans don't have perfect memories, and neither should social
networks~\cite{delete}. Many users already engage in manual auditing and
deletion of old posts~\cite{fbtips2}. A better solution would be to build tools
that let the user manage this more easily through an API: both Twitter and
Facebook provide APIs for post deletion.
%\footnote{Google Plus offers a read-only API.}

@@

\section{Summary}
People have multiple contextual identities. Sharing personal information in
appropriate contexts fosters positive human interaction.  We hope that
contextual identity serves as a useful notion for developers to understand
their users' privacy needs and develop tools to help users manage their
identities.

>>>>

\label{sec:examples}
\subsection{Redistributing information out of context}
Redistributing information out of its original context often leads to
embarrassment~\cite{nissenbaum}.  In November 2007, Facebook Beacon allowed
third-party sites to publish purchases, travel bookings, movie rentals and more
to the user's activity stream.  Poor opt-out and lack of visibility
into what was being published led to user surprise and dismay~\cite{mccarthy,nakashima}.  In December 2007, Google Reader exposed
RSS feeds of user-marked news stories to the user's Google Talk contacts, which
includes everyone with whom a user has chatted whether they be co-workers,
supervisors, or friends. Although this feed was always public, prior to this
launch it was not discoverable, leading to a bad experience for many
users~\cite{helft}. In February 2010, Google Buzz launched, a product that
exposed the user's most frequent Gmail and Google Talk contacts and their
publicly available (through previously less discoverable) news and photos.  The
combination of exposing contacts (which could include abusive ex-husbands,
co-workers, and friends), as well as aggressively linking photos and news
items, resulted in a huge backlash~\cite{fugitivus,buzz}. In September 2012,
Facebook imported old wall posts from 2008 into the new Timeline interface.
Although wall posts were always visible from profile pages, the new Timeline
interface brought old wall posts, which users used to treat as private messages
before the advent of ``Like'' and comment buttons, to the attention of an
audience that the user never anticipated~\cite{timeline}.

@@

The following examples illustrate how users attempt to preserve boundaries
between identities. None of these techniques are failsafe, but they serve as
useful reminders that perfect solutions may not be necessary, especially in the
case where information leaks by casual or accidental inspection.

@@

Using multiple browsers is a useful technique for managing multiple accounts.
Some services support multiple accounts but not multiple login (e.g.,
Twitter). For services that do, the user interface
may be so confusing that it leads to errors, so the best recommendation may be
to use multiple browsers~\cite{yegge}.\footnote{Using multiple
browsers as an alternative to multiple login:
\url{https://support.google.com/accounts/bin/answer.py?hl=en&answer=179235}}
For users who want to separate work and
personal browsing, using multiple browsers is the easiest solution.

@@

Many users have multiple devices and many use them for different purposes.
Some of this difference is due to the nature of the device (e.g.,
GPS and mapping software are probably more often used in mobile devices) and
some may be due to policy (e.g., limiting work activities to a corporate
laptop). Using multiple devices implicitly creates multiple browser states and
thus multiple identities.  However, these identities may still be linked
through authentication data or other techniques.%~\cite{aol}

@@

Several browsers support separation of profile data, including cookies,
history, passwords, and other local storage. Firefox 
%\url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}.}
and Chrome support multiple profiles, though neither of these implementations
is discoverable or easy to use.\footnote{Chrome:
\url{https://support.google.com/chrome/bin/answer.py?hl=en&answer=2364824},
Firefox: \url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}} The
threat model does not include users with malicious intent in the same
household.

@@

Users can explicitly create links between contextual identities, e.g.  linking
to their blog from their Flickr profile, or resharing a blog post via Twitter.
It is also easy to implicitly create links between contextual identities,
sometimes accidentally: generating two isomorphic graphs at different services
is often enough to re-identify an individual~\cite{narayanan1}. The plethora of
cross-posting software suggests that users often want to link
identities.

Building reputation online is a long and arduous process; a user who has built
up high credibility in one social network may want to transfer that credibility
when using a new service by using the same identifier or somehow proving in the
new service that they control other credible identities.  The advent
of verified account mechanisms in Twitter, Google Plus and Facebook suggests
this problem is on the rise.

@@

All five major browsers (Firefox, Chrome, Safari, Internet Explorer, and Opera)
offer synchronizing a subset of browser data across devices.
Multiple cross-browser applications also exist to
synchronize bookmarks and passwords.\footnote{An example of bookmark sync is \url{xmarks.com}, one cloud-based password manager is \url{lastpass.com}.}

@@

\paragraph{Service settings} Service configurations such as Facebook friends,
Google circles and privacy settings are intended for users to self-manage
privacy and identity. However, shifting privacy settings and complex,
interacting features make these configurations unpredictable for many users.
According to Pew Internet, 71\% of users change privacy-related settings; yet
the large number of users who experience regret on social networks indicates
that these settings are not working as intended~\cite{pew3}.

@@

Service providers are highly incentivized to make linking identities easy;
users need more tools to help separate and curate identities. Without
knowing more about how users think about identity, we concentrate solely on
automating manual processes that users already perform.

@@

\paragraph{Expiring posts}
Humans don't have perfect memories, and we question why social networks
do~\cite{delete}. Many users already engage in manual auditing and
deletion of old posts~\cite{fbtips2}. A better solution would be to build tools
that let the user manage this more easily through an API: both Twitter and
Facebook provide APIs for post deletion.
%\footnote{Google Plus offers a read-only API.}

@@

\section{Summary}
People have multiple contextual identities. Sharing personal information in
appropriate contexts fosters positive human interaction and doesn't negate the need or desire for privacy. We hope that
contextual identity serves as a useful notion for developers to understand
their users' privacy needs and develop tools to help users manage their
identities.
